A Data-Driven Framework for Neural Field Modelling

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
added a bit to the conclusion

\section{Discussion}\label{DiscussionSection}
\dean{I MIGHT MOVE THIS BIT TO THE CONCLUSION. ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.

@@

\section{Conclusion}
This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology. \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed... \dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}

>>>>

\section{Discussion}\label{DiscussionSection}

@@

\section{Conclusion}
\dean{I MOVED THIS FROM THE START OF THE DISCUSSION. ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. We have derived a finite-order state-space representation of the neural field equations that allows inference to be performed efficiently. In addition, the mathematical formulation that we have presented scales well with the number of sensors. The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
